---
title: "Make a table for the quickin case"
output: html_notebook
---

It takes a really long time to run those fishSim pops, so I am
just going to report this single rep of them
```{r}
library(tidyverse)

# read the data and unnest it
dat <- read_rds("stored_results/cores16/sim_results_cores_16.rds") %>%
  unnest(cols = c(res))
```

Now we extract the elapsed time in seconds.  Since we are comparing multicore fishSim to
single-core spip, I think this is the best comparison.
```{r}
dat2 <- dat %>%
  mutate(
    spip_elapsed_sim_time = map_dbl(spip_sim_time, 3),
    fishSim_elapsed_sim_time = map_dbl(fishSim_sim_time, 3),
    spip_elapsed_pair_time = map_dbl(spip_pair_time, 3),
    fishSim_elapsed_pair_time = map_dbl(fishSim_pair_time, 3),
  )
```

Now, let's get the columns in the order that we want them, and also
round all the times to the nearest tenth
```{r}
dat3 <- dat2 %>%
  select(
    N,
    spip_size,
    fish_sim_size,
    contains("elapsed_sim"),
    spip_sample_size,
    fish_sim_sample_size,
    contains("elapsed_pair")
  ) %>%
  mutate(
    across(
      .cols = contains("time"),
      .fns = round,
      digits = 1
    )
  )
```



That is good enought to write into LaTeX and format as a table.
```{r}
dir.create("outputs/004", recursive = TRUE, showWarnings = FALSE)
write_delim(
  dat3,
  delim = "&",
  eol = "\\tabularnewline\n",
  file = "outputs/004/sim-table.tex"
)
```
